### 2023-05-28 main.tex
Q0

\begin{align}
	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}{\color{red}=N}\\
	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}={\color{red}N+2L-1}\\
	Q_{2L\phantom{+}}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}
\end{equation}
that is 
\begin{equation}
\begin{split}
Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
&=N+2e_{11}^{tot}(e_{11}^{tot}+1)+(N+2)(e_{11}^{tot}-L)+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
\end{split}
\end{equation} 
we also introduce 
\begin{equation}
	\mathcal{Q}_{2L}=\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{equation}
therefore we can write 
\begin{equation}
	Q_{2L}=Q_{2L}^{0}+\mathcal{Q}_{2L}
\end{equation}
%  It has the property that commute with the equilibrium Hamiltonian.

>>>>

\begin{align}
	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}{\color{red}=N}\\
	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}={\color{red}N+2L-1}\\
	Q_{2L\phantom{+}}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}
\end{equation}
that is 
\begin{equation}
	\begin{split}
	Q_{2L}^{0}&=N(I^{tot}+e_{11}^{tot})+e_{11}^{tot}(2e_{11}^{tot}+I^{tot})-\sum_{k=2}^{N}e_{kk}^{tot}-2N\sum_{k=2}^{N}e_{kk}^{tot}+\sum_{k=2}^{N}\left\{e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+\sum_{j=2}^{N}e_{kj}^{tot}e_{jk}^{tot}\right\}
	\\&=
	(N-NL-2L)I^{tot}+2(N+2)e_{11}^{tot}+2e_{11}^{tot}e_{11}^{tot}+2\sum_{j,k=2}^{N}e_{kj}^{tot}e_{jk}^{tot}
	\end{split}
\end{equation}
%\begin{equation}	
%\begin{split}
%Q_{2L}^{0}&=NI^{tot}+2e_{11}^{tot}(e_{11}^{tot}+I^{tot})-(N+2)\sum_{j=2}^{N}e_{jj}^{tot}+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
%&=N+2e_{11}^{tot}(e_{11}^{tot}+1)+(N+2)(e_{11}^{tot}-L)+2\sum_{i,j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}\\
%\end{split}
%\end{equation} 
we also introduce 
\begin{equation}
	\mathcal{Q}_{2L}=\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{equation}
therefore we can write 
\begin{equation}
	Q_{2L}=Q_{2L}^{0}+\mathcal{Q}_{2L}
\end{equation}
%  It has the property that commute with the equilibrium Hamiltonian.
